A generic and fast C++ optimization framework

### 2017-11-17 paper.tex
Escape mail address for the submission.

\author{
  Shikhar Bhardwaj \\
  Delhi Technological University \\
  Delhi - 110042 \\
  \texttt{shikhar_bt2k15@dtu.ac.in} \\
  \AND
  Yannis Mentekidis \\
  \AND
  Marcus Edel \\
  Free University of Berlin \\
  Arnimallee 7, 14195 Berlin \\
  \texttt{marcus.edel@fu-berlin.de} \\
  \AND
  Ryan R. Curtin \\
  Symantec Corporation \\
  Atlanta, GA, USA 30318 \\
  \texttt{ryan@ratml.org} \\
}

@@

\begin{abstract}
The development of the {\bf mlpack} C++ machine learning library
(\url{http://www.mlpack.org/}) has required the design and implementation of a
flexible, robust optimization system that is able to solve the types of
arbitrary optimization problems that may arise all throughout machine learning
problems.  In this paper, we present the generic optimization framework that we
have designed for mlpack.  A key priority in the design was ease of
implementation of both new optimizers and new objective functions to be
optimized; therefore, implementation of a new optimizer requires only one
method and implementation of a new objective function requires at most four
functions.  This leads to simple and intuitive code, which, for fast prototyping
and experimentation, is of paramount importance.  When compared to
optimization frameworks of other libraries, we find that mlpack's supports more
types of objective functions, is able to make optimizations that other
frameworks do not, and seamlessly supports user-defined objective functions
{\it and} optimizers.
%\begin{itemize}
%  \item It's easy to implement new optimizers.
%  \item It's easy to implement new functions to be optimized.
%  \item This system is more comprehensive than other techniques that may focus
%only on neural networks or single problems.
%  \item This system is also more specific and offers more room for optimization
%than super general systems like scipy.optimize().
%\end{itemize}
%
%This abstract will need to be rewritten.
\end{abstract}

\section{Introduction}

@@

\vspace*{-0.3em}
\section{Optimizer API}
\vspace*{-0.4em}

@@

\vspace*{-0.4em}
{\footnotesize
\begin{verbatim}
  error: static assertion failed: the FunctionType does not have a correct
      definition of a Gradient() function
\end{verbatim}
}
\vspace*{-0.9em}

@@

  \item {\bf Annealing variants:} Simulated Annealing

  \item {\bf Other:} Conditional Gradient Descent, Frank-Wolfe algorithm

>>>>

\author{
  Ryan R. Curtin \\
  Symantec Corporation \\
  Atlanta, GA, USA 30318 \\
  \texttt{ryan@ratml.org} \\
  \And
  Shikhar Bhardwaj \\
  Delhi Technological University \\
  Delhi - 110042 \\
  \texttt{shikhar\char`_bt2k15@dtu.ac.in}
  \And
  Marcus Edel \\
  Free University of Berlin \\
  Arnimallee 7, 14195 Berlin \\
  \texttt{marcus.edel@fu-berlin.de} \\
  \And
  Yannis Mentekidis \\
  mentekid@gmail.com
}

@@

\vspace*{-0.5cm}
\begin{abstract}
The development of the {\bf mlpack} C++ machine learning library
(\url{http://www.mlpack.org/}) has required the design and implementation of a
flexible, robust optimization system that is able to solve the types of
arbitrary optimization problems that may arise all throughout machine learning
problems.  In this paper, we present the generic optimization framework that we
have designed for mlpack.  A key priority in the design was ease of
implementation of both new optimizers and new objective functions to be
optimized; therefore, implementation of a new optimizer requires only one
method and implementation of a new objective function requires at most four
functions.  This leads to simple and intuitive code, which, for fast prototyping
and experimentation, is of paramount importance.  When compared to
optimization frameworks of other libraries, we find that mlpack's supports more
types of objective functions, is able to make optimizations that other
frameworks do not, and seamlessly supports user-defined objective functions
{\it and} optimizers.
%\begin{itemize}
%  \item It's easy to implement new optimizers.
%  \item It's easy to implement new functions to be optimized.
%  \item This system is more comprehensive than other techniques that may focus
%only on neural networks or single problems.
%  \item This system is also more specific and offers more room for optimization
%than super general systems like scipy.optimize().
%\end{itemize}
%
%This abstract will need to be rewritten.
\end{abstract}

\vspace*{-0.5cm}
\section{Introduction}

@@

\vspace*{-0.4em}
\section{Optimizer API}
\vspace*{-0.5em}

@@

\vspace*{-0.5em}
{\footnotesize
\begin{verbatim}
  error: static assertion failed: the FunctionType does not have a correct
      definition of a Gradient() function
\end{verbatim}
}
\vspace*{-0.9em}

@@

  \item {\bf Other:} Conditional Gradient Descent, Frank-Wolfe algorithm, Simulated Annealing
